### 2013-01-20 draft.tex
contents fixed
save

\documentclass[12pt,a4paper,oneside,titlepage]{article}
\usepackage[utf8]{inputenc}
\usepackage[english, russian]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{textcase} 
\usepackage{tocloft}
\usepackage{lastpage}
\usepackage[left=3.5cm,right=1cm,top=2cm,bottom=1.2cm]{geometry}
\author{Kostenko}
\setcounter{tocdepth}{3}%для глубины страницы содаржения
\renewcommand{\baselinestretch}{1.25}
\renewcommand{\cftsecleader}{\cftdotfill{\cftdotsep}} % точки в содержании для секций
\bibliographystyle{unsrt}
\begin{document}
{
\thispagestyle{empty}
\newpage
\centering

@@

Nowadays, paradigm proposed D. Marr \cite{marr} is used in image processing.
Point of this one is to process images in sequence:
\begin{enumerate}
  \item image pre-processing
  \item segmentation
  \item distinguish of the geometric structure
  \item determine the semantics
\end{enumerate}
In other words, processing of low-level should be performed at first, then intermediate-level processing and then high-level processing.

In the general form, motion analysis is comparison of consecutive images of the observed scene.

@@

\newpage
\section*{Conclusion}
\addcontentsline{toc}{section}{Conclusion}
1 pages
%

>>>>

\documentclass[12pt,a4paper,oneside,titlepage]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{textcase} 
\usepackage{tocloft}
\usepackage{lastpage}
\usepackage[left=3.5cm,right=1cm,top=2cm,bottom=2cm]{geometry}
\author{Kostenko}
\setcounter{tocdepth}{3}%для глубины страницы содаржения
\renewcommand{\baselinestretch}{1.25}
\renewcommand{\cftsecleader}{\cftdotfill{\cftdotsep}} % точки в содержании для секций
\bibliographystyle{unsrt}
\begin{document}
{
\thispagestyle{empty}
\newpage
\centering

@@

Nowadays, paradigm is used in image processing proposed by D. Marr \cite{marr}.
Point of this one is to process images in sequence:
\begin{enumerate}
  \item image pre-processing
  \item segmentation
  \item distinguish of the geometric structure
  \item determine the semantics
\end{enumerate}

In other words, processing of low-level should be performed at first, then intermediate-level processing and then high-level processing.

In the general form, motion analysis is comparison of consecutive images of the observed scene.
It means the difference between the current frame and the previous one.
As a result of this operation, we have contours of a moving object.
This is one of the basic ideas of our work.

@@

\newpage
\section*{Conclusion}
\addcontentsline{toc}{section}{Conclusion}
1 page
